Results

### 2019-02-26 02_analysis.Rmd
Use RAW STAN for better analysis
No more triple interaction terms!

---
title: "Results"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args: [
      "--default-image-extension=png"
    ]
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

@@

  factor_summary <- data_frame(x) %>% 
    count(x) %>%
    mutate(pct = n / sum(n),
           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
           x = factor(x, levels = x_levels, ordered = TRUE))

@@

  output <- data_frame(spark = md_img, summary = inline_summary)
  return(output)
}

@@

## Prior favorability towards NGOs

```{r fig-ngo-favorability, fig.width=7, fig.height=4}
favorability_cols <- data_frame(value = c("Very unfavorable", "Unfavorable", "Neutral",
                                          "Favorable", "Very favorable"),
                                color = ngo_pal("ordered")(5))

ngo_favorability_raw <- results %>%
  select(favor_humanitarian, favor_human_rights, favor_development) %>% 
  gather(variable, value) %>% 
  count(variable, value) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  left_join(favorability_cols, by = "value") %>%
  mutate(clean_name = str_replace(clean_name, "towards", "towards\n")) %>% 
  mutate(value = factor(value, levels = levels(results$favor_humanitarian), ordered = TRUE),
         clean_name = fct_inorder(clean_name, ordered = TRUE)) %>%
  arrange(value) %>% 
  mutate(color = fct_inorder(color, ordered = TRUE))

ngo_favorability_high <- ngo_favorability_raw %>% 
  filter(!str_detect(value, "nfav")) %>% 
  mutate(n = ifelse(value == "Neutral", n / 2, n),
         n_plot = n,
         value = fct_rev(value), color = fct_rev(color))

ngo_favorability_low <- ngo_favorability_raw %>% 
  filter(str_detect(value, "nfav") | value == "Neutral") %>% 
  mutate(n = ifelse(value == "Neutral", n / 2, n),
         n_plot = -n)

ggplot(mapping = aes(x = n_plot, y = clean_name, fill = color)) +
  geom_barh(data = ngo_favorability_high, stat = "identity") +
  geom_barh(data = ngo_favorability_low, stat = "identity") +
  geom_vline(xintercept = 0, color = "black") +
  scale_x_continuous(labels = abs) +
  scale_fill_identity(labels = levels(ngo_favorability_raw$value),
                      breaks = levels(ngo_favorability_raw$color),
                      guide = "legend", name = NULL) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank())
```

@@

plot_donate_summary <- ggplot(donate_summary, aes(x = n, y = donate_likely, 
                                                  fill = highlight)) +
  geom_barh(stat = "identity") +
  scale_x_continuous(sec.axis = sec_axis(~ . / sum(donate_summary$n),
                                         labels = percent)) +
  scale_fill_manual(values = ngo_cols("green", "blue", name = FALSE), guide = FALSE) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

# Interpreting interactions in models

Ordinarily, people use ANOVA to analyze 3-way, 2 × 2 × 2 factorial designs, [like this](https://mypages.valdosta.edu/mwhatley/3600/2x2x2.htm). A more flexible ([yet identical!](https://www.theanalysisfactor.com/why-anova-and-linear-regression-are-the-same-analysis/)) way to do this is to use a regular regression model with interaction terms for each of the conditions, like so (here we use three, since we can use simper models to get averages for the larger umbrella groups, like just crackdowns and crackdown + issue):

- Model 1:

    $$
    y = \beta_0 + \beta_1 \text{Crackdown}
    $$

- Model 2:

    $$
    \begin{aligned}
    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue } + \\
    & \beta_3 \text{Crackdown} \times \text{Issue}
    \end{aligned}
    $$

- Model 3:

    $$
    \begin{aligned}
    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue} + \beta_3 \text{Funding } + \\
    & \beta_4 \text{Crackdown} \times \text{Issue } + \\
    & \beta_5 \text{Crackdown} \times \text{Funding } + \\
    & \beta_6 \text{Issue} \times \text{Funding } + \\
    & \beta_7 \text{Crackdown} \times \text{Issue} \times \text{Funding}
    \end{aligned}
    $$

Adding different combinations of the coefficients provides the average values for each combination of factors, which corresponds to the average likelihood and amount donated table above.

```{r interaction-interpretation, results="asis"}
model1 <- "1"
model2 <- "2"
model3 <- "3"

interpretation <- tribble(
  ~Model, ~`Coefficients to add together`,
  model3, "Intercept",
  model3, "Intercept + Funding",
  model2, "Intercept",
  model3, "Intercept + Issue",
  model3, "Intercept + Issue + Funding + (Issue × Funding)",
  model2, "Intercept + Issue",
  model1, "Intercept",
  model3, "Intercept + Crackdown",
  model3, "Intercept + Crackdown + Funding + (Crackdown × Funding)",
  model2, "Intercept + Crackdown",
  model3, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
  model3, "Intercept + Crackdown + Issue + Funding + (Crackdown × Issue) + (Crackdown × Funding) + (Issue × Funding) + (Crackdown × Issue × Funding)",
  model2, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
  model1, "Intercept + Crackdown"
)

conditions_summary_clean %>% 
  select(1:3) %>% 
  slice(-n()) %>% 
  bind_cols(interpretation) %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Combinations of coefficients to add to determine means across experimental conditions {#tbl:coefficients-to-add}") %>% 
  cat(file = here("output", "tables", "tbl-coefficients-to-add.md"))
```

@@

# Amount donated

## Models

```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
m_amount_c <- stan_glm(amount_donate ~ crackdown,
                       data = results, family = gaussian(),
                       prior = cauchy(location = 0, scale = 2.5),
                       prior_intercept = cauchy(location = 0, scale = 10),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)

m_amount_cif <- update(m_amount_c, . ~ . + 
                         issue + funding + crackdown * issue + crackdown * funding + 
                         issue * funding + crackdown * issue * funding)

# Models with just issue and just funding
m_amount_i <- update(m_amount_c, . ~ issue)
m_amount_f <- update(m_amount_c, . ~ funding)
```

```{r tbl-models-amount, warning=FALSE, results="asis"}
# Get subset of coefficients
coefs_to_include <- list(m_amount_c, m_amount_ci, m_amount_cif) %>% 
  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)

huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = here("output", "tables", "tbl-models-amount.md"))
```

## Predicted medians

The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution (like, [they didn't even want to invent it, and then when they did they wanted to hide it](https://github.com/stan-dev/rstanarm/issues/85), and it has a big warning in the documentation). But this approach here mirrors using `predict()` to combine all the coefficients and intercept terms in a regular frequentist linear model and it's probably appropriate for this situation because all the coefficients are actually linked together behind the scenes and create group mean estimates. If I use the full force of `posterior_predict()`, I add more uncertainty with each added coefficient (so in a 2×2×2 version, the 8th condition is actually the sum of all 8 coefficients, which means it gets 8 levels of uncertainity, which is probably excessive). But we do it both ways too, just to be on the safe side.

```{r amount-median-c}
newdata_conditions_c <- results %>% expand(nesting(crackdown))

chains_fitted_c <- posterior_linpred(m_amount_c, 
                                     newdata = newdata_conditions_c)

# posterior_fit <- posterior_predict(m_amount_c, 
#                                    newdata = newdata_conditions_c,
#                                    draws = 50, seed = BAYES_SEED)

coef_summary_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(chains_fitted_c, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

# newdata <- newdata_conditions %>% 
#   bind_cols(tidyMCMC(posterior_fit, estimate.method = "median",
#                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_amount_c <- ggplot(coef_summary_c, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

```{r amount-median-i}
newdata_conditions_i <- results %>% expand(nesting(issue))

chains_fitted_i <- posterior_linpred(m_amount_i, 
                                     newdata = newdata_conditions_i)

coef_summary_i <- newdata_conditions_i %>% 
  bind_cols(tidyMCMC(chains_fitted_i, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

```{r amount-median-f}
newdata_conditions_f <- results %>% expand(nesting(funding))

chains_fitted_f <- posterior_linpred(m_amount_f, 
                                     newdata = newdata_conditions_f)

coef_summary_f <- newdata_conditions_f %>% 
  bind_cols(tidyMCMC(chains_fitted_f, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

```{r amount-median-ci}
newdata_conditions_ci <- results %>% expand(nesting(crackdown, issue))

chains_fitted_ci <- posterior_linpred(m_amount_ci, 
                                      newdata = newdata_conditions_ci)

coef_summary_ci <- newdata_conditions_ci %>% 
  bind_cols(tidyMCMC(chains_fitted_ci, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_amount_ci <- ggplot(coef_summary_ci, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("blue")) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue)
```

```{r amount-median-cif}
newdata_conditions_cif <- results %>% expand(nesting(crackdown, issue, funding))

chains_fitted_cif <- posterior_linpred(m_amount_cif, 
                                       newdata = newdata_conditions_cif)

coef_summary_cif <- newdata_conditions_cif %>% 
  bind_cols(tidyMCMC(chains_fitted_cif, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_amount_cif <- ggplot(coef_summary_cif, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("red")) +
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue + funding)
```

```{r plot-single-amount-medians, warning=FALSE, fig.width=7, fig.height=2.5}
coef_summary_singles <- bind_rows(coef_summary_c, coef_summary_i, coef_summary_f) %>% 
  gather(condition, value, crackdown, issue, funding) %>% 
  filter(!is.na(value)) %>% 
  mutate(value = fct_inorder(value, ordered = TRUE),
         condition = fct_inorder(str_to_title(condition), ordered = TRUE))

>>>>

---
title: "Results"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstan)
library(tidybayes)
library(broom)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

@@

  factor_summary <- tibble(x) %>% 
    count(x) %>%
    mutate(pct = n / sum(n),
           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
           x = factor(x, levels = x_levels, ordered = TRUE))

@@

  output <- tibble(spark = md_img, summary = inline_summary)
  return(output)
}

@@

@@

plot_donate_summary <- ggplot(donate_summary, aes(x = n, y = donate_likely, 
                                                  fill = highlight)) +
  geom_barh(stat = "identity") +
  scale_x_continuous(sec.axis = sec_axis(~ . / sum(donate_summary$n),
                                         labels = percent_format(accuracy = 1))) +
  scale_fill_manual(values = ngo_cols("green", "blue", name = FALSE), guide = FALSE) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

```{r all-datasets-nested}
all_models <- tribble(
  ~title, ~df,
  "Crackdown", results,
  # Ha, cheat here by renaming the issue and funding columns to crackdown. 
  # All other tests are based on the crackdown column except these two, so
  # rather than build all sorts of convoluted arguments and functions, we just
  # rename these as issue and funding
  "Issue", mutate(results, crackdown = issue),
  "Funding", mutate(results, crackdown = funding),
  # Create all the nested conditions
  "Human rights | Crackdown", filter(results, issue == "Human rights"),
  "Humanitarian assistance | Crackdown", filter(results, issue != "Human rights"),
  "Government | Crackdown", filter(results, funding == "Government"),
  "Private | Crackdown", filter(results, funding == "Private"),
  "Human rights | Government | Crackdown", filter(results, issue == "Human rights", funding == "Government"),
  "Human rights | Private | Crackdown", filter(results, issue == "Human rights", funding == "Private"),
  "Humanitarian assistance | Government | Crackdown", filter(results, issue != "Human rights", funding == "Government"),
  "Humanitarian assistance | Private | Crackdown", filter(results, issue != "Human rights", funding == "Private")
) 
```

# Treatment effects: Likelihood of donation

This time around, we're not using interactionful regression models to calculate all these differences in groups. Instead we use real live Stan code to estimate the differences in group means and proportions!

## Priors and models

We estimate the proportion of people responding that they'd be likely to donate to the organization with a binomial distribution, with a prior $\theta$ distribution of $\text{Beta}(5, 5)$. We build the following model in Stan:

$$
\begin{aligned}
n_{\text{group 1, group 2}} &\sim \text{Binomial}(n_{\text{total in group}}, \theta_{\text{group}}) &\text{[likelihood]}\\
\text{Difference} &= n_{\text{group 2}} - n_{\text{group 1}} &\text{[difference in proportions]} \\
n &: \text{Number likely to donate} \\
\\
\theta_{\text{group 1, group 2}} &\sim \text{Beta}(5, 5) &\text{[prior prob. of being likely to donate]}
\end{aligned}
$$

```{r priors-likely, fig.width=2.75, fig.height=1.5, fig.align="center"}
likely_theta <- ggplot(data = tibble(x = c(0, 1)), aes(x = x)) +
  geom_area(stat = "function", fun = dbeta, args = list(shape1 = 5, shape2 = 5), 
            fill = "grey80", color = "black") +
  labs(x = expression(Probability ~ of ~ being ~ likely ~ to ~ donate ~ (theta)), y = "Density") +
  annotate(geom = "label", x = 0.5, y = 1, label = "Beta(5, 5)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)
likely_theta
```

## Differences

```{r run-likely-models, results="hide", cache=TRUE}
# This takes forever because of C++ compiling and actual MCMC sampling, so this
# chunk is cached

# Compile model
donate_likely <- stan_model(here("lib", "donate_likely.stan"))

# Sample from the compiled model
all_models_likely_run <- all_models %>% 
  # Simplify data for sending to Stan
  mutate(stan_data_counts = df %>% map(~ {
    df_counts <- .x %>% 
      count(crackdown, donate_likely_bin) %>% 
      group_by(crackdown) %>% 
      mutate(total = sum(n)) %>% 
      filter(donate_likely_bin == "Likely")

    return(list(
      n_total_1 = df_counts$total[1],
      n_total_2 = df_counts$total[2],
      n_likely_1 = df_counts$n[1],
      n_likely_2 = df_counts$n[2]
    ))
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data_counts %>% map(~ {
    sampling(donate_likely, data = .x, control = list(max_treedepth = 15),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

# Extract stuff
all_models_likely <- all_models_likely_run %>% 
  # Extract posterior chains
  mutate(posterior_chains_long = map(model, ~ {
      .x %>% gather_draws(theta_1, theta_2, theta_diff, pct_change)
  })) %>% 
  mutate(posterior_chains_wide = map(model, ~ {
      .x %>% spread_draws(theta_1, theta_2, theta_diff, pct_change)
  })) %>% 
  # Get HDI medians in tidy form
  mutate(tidy = posterior_chains_long %>% map(~ {
    .x %>% median_hdci() %>% to_broom_names()
  }))
```

```{r plot-likely-diffs, warning=FALSE, fig.width=6, fig.height=8}
tidied_diffs_likely <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

level1_likely <- tidied_diffs_likely %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title))

plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Median difference in donation likelihood", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

level2_likely <- tidied_diffs_likely %>% 
  filter(category == "Level 2") %>%
  mutate(condition = case_when(
    title %in% c("Human rights", "Humanitarian assistance") ~ "Issue",
    title %in% c("Government", "Private") ~ "Funding"
  )) %>% 
  mutate(facet_title = case_when(
    title %in% c("Human rights", "Humanitarian assistance") ~ paste(title, "issues"),
    title %in% c("Government", "Private") ~ paste(title, "funding")
  )) %>% 
  mutate(title = case_when(
    title %in% c("Humanitarian assistance", "Private") ~ "",
    TRUE ~ "Crackdown −\nNo crackdown")
  )

plot_diff_likely_b <- ggplot(filter(level2_likely, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Median difference in donation likelihood", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

level3_likely <- tidied_diffs_likely %>% 
  filter(category == "Level 3") %>%
  separate(title, c("issue", "funding"), sep = " \\| ") %>%
  mutate(issue = paste(issue, "issues"),
         funding = paste(funding, "funding")) %>% 
  mutate(facet_title = paste0(issue, "\n", funding)) %>% 
  mutate(title = case_when(
    funding == "Private funding" ~ "",
    TRUE ~ "Crackdown −\nNo crackdown")
  )

plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Median difference in donation likelihood", y = NULL, tag = "D") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

plot_diffs_likely_all <- plot_diff_likely_a / 
  (plot_diff_likely_b / plot_diff_likely_c) / 
  plot_diff_likely_d

plot_diffs_likely_all

plot_diffs_likely_all %T>% 
  ggsave(., filename = here("output", "figures", "likely-diffs.pdf"),
         width = 6, height = 8, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "likely-diffs.png"),
         width = 6, height = 8, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy <- all_models_likely %>% 
  unnest(tidy) %>% 
  filter(term %in% c("theta_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

tbl_likely_probs <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  group_by(title) %>% 
  summarize(p.greater0 = mean(.value > 0),
            p.less0 = mean(.value < 0),
            p.diff.not0 = ifelse(median(.value) > 0, p.greater0, p.less0)) %>% 
  ungroup()

tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title)) %>% 
  select(`Frame` = title, `∆` = theta_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation across single conditions; values represent posterior medians {#tbl:likely-diffs-1}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-1.md"))
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  select(Frame = title_clean, `∆` = theta_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-2}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-2.md"))
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  select(`Issue frame` = Issue, `Funding frame` = Funding, `∆` = theta_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-3}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-3.md"))
```

@@

# Treatment effects: Amount donated

## Priors and models

Following [John Kruschke's "Bayesian Estimation Supersedes the t-test (BEST)" procedure](http://www.indiana.edu/~kruschke/BEST/BEST.pdf), we estimate means for each group with a t-distribution. We use the following priors for the distribution parameters:

$$
\begin{aligned}
x_{\text{group 1, group 2}} &\sim \text{Student } t(\nu, \mu, \sigma) &\text{[likelihood]}\\
\text{Difference} &= x_{\text{group 2}} - x_{\text{group 1}} &\text{[difference in means]} \\
x &: \text{Mean amount donated} \\
\\
\nu &\sim \text{Exponential}(1 / 29) &\text{[prior normality]} \\
\mu_{\text{group 1, group 2}} &\sim \mathcal{N}(\bar{x}_{\text{group 1, group 2}}, 10) &\text{[prior donation mean per group]}\\
\sigma_{\text{group 1, group 2}} &\sim \text{Cauchy}(0, 1)&\text{[prior donation sd per group]}
\end{aligned}
$$

```{r priors-amounts, fig.width=8, fig.height=1.5}
amount_nu <- ggplot(data = tibble(x = c(0, 200)), aes(x = x)) +
  geom_area(stat = "function", fun = dexp, args = list(rate = 1/29), 
            fill = "grey80", color = "black") +
  labs(x = expression(Normality ~ parameter ~ (nu)), y = "Density") +
  annotate(geom = "label", x = 100, y = 0.009, 
           label = "Exponential(1/29)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)

amount_mu <- ggplot(data = tibble(x = c(0, 100)), aes(x = x)) +
  geom_area(stat = "function", fun = dnorm, args = list(mean = 50, sd = 10),
            fill = "grey80", color = "black") +
  scale_x_continuous(breaks = c(seq(0, 100, 25)),
                     labels = c("−$50", "−$25", "Group average", "+$25", "+$50")) +
  annotate(geom = "label", x = 50, y = 0.01, label = "N(bar(x), 10)", 
           parse = TRUE, size = pts(9)) +
  labs(x = expression(Average ~ donated ~ (mu)), y = NULL) +
  theme_ngos(base_size = 9, density = TRUE)

amount_sigma <- ggplot(data = tibble(x = c(0, 10)), aes(x = x)) +
  geom_area(stat = "function", fun = dcauchy, args = list(location = 0, scale = 1),
            fill = "grey80", color = "black") +
  scale_x_continuous(labels = dollar) +
  annotate(geom = "label", x = 5, y = 0.08, label = "Cauchy(0, 1)", size = pts(9)) +
  labs(x = expression(SD ~ donated ~ (sigma)), y = NULL) +
  theme_ngos(base_size = 9, density = TRUE)

amount_nu + amount_mu + amount_sigma
```

## Differences

```{r run-amount-models, results="hide", cache=TRUE}
# This takes forever because of C++ compiling and actual MCMC sampling, so this
# chunk is cached

# Compile model
amount_donated_best <- stan_model(here("lib", "amount_donated_best.stan"))

# Sample from the compiled model
all_models_amount_run <- all_models %>% 
  # Simplify data for sending to Stan
  mutate(stan_data = df %>% map(~ {
    select(.x, amount = amount_donate, group = crackdown)
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data %>% map(~ {
    sampling(amount_donated_best, data = compose_data(.x),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

# Extract stuff
all_models_amount <- all_models_amount_run %>% 
  # Extract posterior chains
  mutate(posterior_chains_long = map2(model, stan_data, ~ {
    .x %>% 
      recover_types(.y) %>% 
      gather_draws(mu[group], sigma[group], mu_diff, pct_change, cohen_d, cles, nu, log10nu)
  })) %>% 
  mutate(posterior_chains_wide = map2(model, stan_data, ~ {
    .x %>% 
      recover_types(.y) %>% 
      spread_draws(mu[group], sigma[group], mu_diff, pct_change, cohen_d, cles, nu, log10nu)
  })) %>% 
  # Get HDI medians in tidy form
  mutate(tidy = posterior_chains_long %>% map(~ {
    .x %>% median_hdci() %>% to_broom_names()
  }))
```

```{r plot-amount-diffs, warning=FALSE, fig.width=6, fig.height=8}
# This will generate a warning because unnest() puts the crackdown values into
# one column and we cheated by renaming issue and funding as crackdown, so it
# gets mad when combining the factors in crackdown with those in issue and
# funding. But because we only care about the diffs, we don't actually need the
# category labels here, so it's all good.
tidied_diffs_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "mu_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

level1_amount <- tidied_diffs_amount %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title))

plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_vline(xintercept = 0) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Median difference in amount donated", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

level2_amount <- tidied_diffs_amount %>% 
  filter(category == "Level 2") %>%
  mutate(condition = case_when(
    title %in% c("Human rights", "Humanitarian assistance") ~ "Issue",
    title %in% c("Government", "Private") ~ "Funding"
  )) %>% 
  mutate(facet_title = case_when(
    title %in% c("Human rights", "Humanitarian assistance") ~ paste(title, "issues"),
    title %in% c("Government", "Private") ~ paste(title, "funding")
  )) %>% 
  mutate(title = case_when(
    title %in% c("Humanitarian assistance", "Private") ~ "",
    TRUE ~ "Crackdown −\nNo crackdown")
  )

plot_diff_amount_b <- ggplot(filter(level2_amount, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Median difference in amount donated", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())
